Pre-/Post-Trikafta (Prospective)

### 2022-11-01 Christine Chan/Pre-post Trikafta Prospective/pre_post_trikafta_prospective_analysis.Rmd
manuscript changes for CFRD and ETI

---
title: "Pre-/Post-Trikafta (Prospective)"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(cgmanalysis)
library(AGD)
library(pracma)
library(corrplot)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/CF")
```

@@

```{r results='asis'}
t2_vars = c("A1C.result","Weight..kg.","weightz","BMIz","FEV1..","FVC....",
            "trikafta_duration","Group","Glucose.0.minute",
            "Glucose.60.min","Glucose.120.min","c.peptide.0.minute",
            "`Glucose iAUC`","`C Peptide iAUC`","`Insulin iAUC`",
            "`C Peptide Index`","Matsuda",
            "`Adapted Matsuda`","`C Peptide ODI`","`ODI (Cpeptide index x Matsuda)`",
            "iAUC_ratio","homa2B","homa2S","homa2IR",
            "Tissue..g.","Total.Fat.Mass....","Fat.Body.Mass..g.","Fat.Free.Mass..g.",
            "Lean.Body.Mass..g.","Total.Mass..kg.","Fat.Free.Mass..",
            "Fat.Mass.Index..FMI...","Lean.body.mass.fat.mass..LBM.FM.",
            "Fat.Free.Mass.Index...FFMI.","Lean.Body.Mass.Index..LBMI.",
            "BMD.Total.z.score","BMD.Subtotal.z.score",
            "DXA.FMI.calculated.z.score","DXA.LBMI.calculated.z.score","total_sensor_readings",
            "mean_sensor","max_sensor","min_sensor","percent_time_70_180",
            "percent_time_over_140","percent_time_over_180","percent_time_over_250",
            "percent_time_under_70","percent_time_under_54","standard_deviation","cv","r_mage")
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p <- paired(f,data = df, id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F,cat.test = "mcnemar",
            control = tableby.control(numeric.stats = c("Nmiss", "medianq1q3", "range")),)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

@@

# Table 4: Prior Modulator Use

Unable to perform statistical tests due to too many missing values.

@@

```{r}
ggplot(df,aes(x = Event.Name, y = A1C.result,fill = Event.Name)) + 
  geom_boxplot(coef=0,alpha = 0.5,outlier.shape = NA) + geom_jitter(width = 0.15) + 
  xlab("Visit") + ylab("HbA1c (%)") + 
  theme_bw() + theme(legend.position = "none") +
  scale_fill_grey()
```

>>>>

---
title: "Pre-/Post-Trikafta (Prospective)"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 5
    toc_float: yes
---

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(cgmanalysis)
library(AGD)
library(pracma)
library(corrplot)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/Work/Vigers/CF")
```

@@

```{r results='asis'}
t2_vars = c("Age.at.visit.","A1C.result","Weight..kg.","weightz","BMI","BMIz",
            "FEV1..","FVC....","trikafta_duration","Group","Glucose.0.minute",
            "Glucose.60.min","Glucose.120.min","c.peptide.0.minute",
            "`Glucose iAUC`","`C Peptide iAUC`","`Insulin iAUC`",
            "`C Peptide Index`","Matsuda",
            "`Adapted Matsuda`","`C Peptide ODI`","`ODI (Cpeptide index x Matsuda)`",
            "iAUC_ratio","homa2B","homa2S","homa2IR",
            "Tissue..g.","Total.Fat.Mass....","Fat.Body.Mass..g.","Fat.Free.Mass..g.",
            "Lean.Body.Mass..g.","Total.Mass..kg.","Fat.Free.Mass..",
            "Fat.Mass.Index..FMI...","Lean.body.mass.fat.mass..LBM.FM.",
            "Fat.Free.Mass.Index...FFMI.","Lean.Body.Mass.Index..LBMI.",
            "BMD.Total.z.score","BMD.Subtotal.z.score",
            "DXA.FMI.calculated.z.score","DXA.LBMI.calculated.z.score","total_sensor_readings",
            "mean_sensor","max_sensor","min_sensor","percent_time_70_180",
            "percent_time_over_140","percent_time_over_180","percent_time_over_250",
            "percent_time_under_70","percent_time_under_54","standard_deviation","cv","r_mage")
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p <- paired(f,data = df, id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F,cat.test = "mcnemar",
            control = tableby.control(numeric.stats = c("Nmiss", "medianq1q3", "range")),)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

@@

# Prior Modulator Use

The following tables include 11 people previously on modulators and 9 not previously on modulators.

## Table 4a: Pre-/Post-ETI Stratified by Previous Use

```{r results='asis'}
df$prev = 
  factor(paste(df$Kalydeco,df$Symdeko, df$Orkambi),
         levels = c("No No No","No No Yes","No Yes No","Yes No No"),
         labels = c("No","Yes","Yes","Yes")
  )
df = df %>% group_by(Study.ID) %>% mutate(`Previous Modulator` = prev[Event.Name == "Visit 1"])

prior_mod_vars = t2_vars[as.numeric(which(colSums(is.na(df[,gsub("`","",t2_vars)]))==0))]
f = as.formula(paste0("Event.Name ~ ",paste0(prior_mod_vars,collapse = "+")))

p <- paired(f,data = df, id = Study.ID,numeric.test = "signed.rank",cat.test = "mcnemar",signed.rank.exact = F,
            strata = `Previous Modulator`,control = tableby.control(numeric.stats = c("Nmiss", "medianq1q3", "range")))
summary(p,pfootnote = T,labelTranslations = newlabels)
```

## Table 4b: Previous Use vs. Not - Baseline

```{r results='asis'}
baseline = df %>% filter(Event.Name == "Visit 1")
f = as.formula(paste0("`Previous Modulator` ~ ",paste0(prior_mod_vars,collapse = "+")))
t = tableby(f,numeric.test = "kwt",data = baseline,
            control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))))
summary(t,digits = 2,labelTranslations = newlabels,pfootnote=TRUE)
```

## Table 4c: Previous Use vs. Not - Follow Up

```{r results='asis'}
visit2 = df %>% filter(Event.Name == "Visit 2")
t = tableby(f,numeric.test = "kwt",data = visit2,
            control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))))
summary(t,digits = 2,labelTranslations = newlabels,pfootnote=TRUE)
```

@@

```{r}
ggplot(df,aes(x = Event.Name, y = A1C.result,fill = Event.Name)) + 
  geom_boxplot(coef=0,alpha = 0.5,outlier.shape = NA) + 
  geom_point(alpha = 0.3) + 
  geom_line(aes(group = Study.ID),alpha = 0.3) + 
  xlab("Visit") + ylab("HbA1c (%)") + 
  theme_bw() + 
  theme(legend.position = "none",axis.title.x=element_blank()) +
  scale_fill_grey()
```
